Effects of Weather on Maize Yield in Kenya

### 2019-01-17 presentations/January2019/presentation1.tex
slidy

\frametitle{Mixed effects estimates:}\label{Results} 
{\begin{threeparttable}
\begin{footnotesize}
\caption*{Yield as dependent variable\hfill exponents of the coefficients: $\exp{\beta}$}
%KEN11dK  KEN11dK_ASAL    KEN11dK_nonASAL										
\label{KenARe11_exponents} 
\setstretch{1.33}
\begin{tabular}{llll} 
  \textbf{Fixed effects:}&\textit{\textbf{All counties}}&\textit{\textbf{ASAL}}&\textit{\textbf{non-ASAL}}\\
\vspace{-0.2cm}Intercept&$1.296^{***}$&$1.272^{*}$&$1.408^{**}$\\
 \vspace{-0.2cm}Prec. total&$1.081^{*}$&$1.007^{}$&$1.277^{***}$\\
  \vspace{-0.2cm}Prec. total sq.&$0.973^{*}$&$1.003$&$0.881^{***}$\\
 \vspace{-0.2cm}Prec. c. of var.&$0.924^{\bullet}$&$0.970$ &$0.907^{}$\\
 \vspace{-0.2cm}Dry spell -length in days&$0.935^{*}$&$0.834^{**}$&$ 0.988^{}$\\
 \vspace{-0.2cm}Dry spells $\geq~4$ days\tnote{b}&$0.939^{*}$&$0.855^{**}$&$0.989^{}$\\
 \vspace{-0.2cm}Temp. - average&$0.820^{***}$&$0.808^{*}$&$0.880$ $^{}$\\
 \vspace{-0.2cm}Temp. c. of var.&$1.043^{\bullet}$&$1.032$&$1.060$ ${*}$\\[2mm]
  \hline
\textit{Number of observations:}  &\multicolumn{1}{c}{$1300$}&\multicolumn{1}{c}{$698$}&\multicolumn{1}{c}{$602$}
\\
\end{tabular} 
 \begin{tablenotes}
  \begin{footnotesize}
    \item \textit{Notes:} Standard errors in brackets; \hfill $^{\bullet}~p<0.1$; $^{*}~p<0.05$; $^{**}~p<0.01$; $^{***}~p<0.001$
  \end{footnotesize}
\end{tablenotes}
\end{footnotesize}
  \end{threeparttable}\par }
\end{frame}

@@

>>>>

\frametitle{Mixed effects estimates:}\label{Results} 
{\begin{threeparttable}
\begin{footnotesize}
\caption*{\small Dependent variable: yield, coefficients in the exponents: $\mathit{e}^{\beta}$}
%KEN11dK  KEN11dK_ASAL    KEN11dK_nonASAL										
\label{KenARe11_exponents} 
\setstretch{1.33}
\begin{tabular}{llll}\hline
&\multicolumn{3}{c}{\textit{Sample:}}\\
&\multicolumn{1}{c}{\textit{(I)}}&\multicolumn{1}{c}{\textit{(II)}}&\multicolumn{1}{c}{\textit{(III)}}\\
  \textbf{Fixed effects:}&\textit{\textbf{All counties}}&\textit{\textbf{ASAL}}&\textit{\textbf{non-ASAL}}\\
  \hline
\vspace{-0.2cm}Intercept&$1.296^{***}$&$1.272^{*}$&$1.408^{**}$\\
 \vspace{-0.2cm}Prec. total&$1.081^{*}$&$1.007^{}$&$1.277^{***}$\\
  \vspace{-0.2cm}Prec. total sq.&$0.973^{*}$&$1.003$&$0.881^{***}$\\
 \vspace{-0.2cm}Prec. c. of var.&$0.924^{\bullet}$&$0.970$ &$0.907^{}$\\
 \vspace{-0.2cm}Dry spell -length in days&$0.935^{*}$&$0.834^{**}$&$ 0.988^{}$\\
 \vspace{-0.2cm}Dry spells $\geq~4$ days\tnote{b}&$0.939^{*}$&$0.855^{**}$&$0.989^{}$\\
 \vspace{-0.2cm}Temp. - average&$0.820^{***}$&$0.808^{*}$&$0.880$ $^{}$\\
 \vspace{-0.2cm}Temp. c. of var.&$1.043^{\bullet}$&$1.032$&$1.060$ ${*}$\\[2mm]
  \hline
\textit{Number of observations:}  &$1300$&$698$&$602$
\\
\end{tabular} 
 \begin{tablenotes}
  \begin{footnotesize}
  \item Standard errors in brackets \\
    $^{\bullet}~p<0.1$; $^{*}~p<0.05$; $^{**}~p<0.01$; $^{***}~p<0.001$
  \end{footnotesize}
\end{tablenotes}
\end{footnotesize}
  \end{threeparttable}\par }
  \setstretch{1}
\end{frame}

@@

\begin{itemize}
\color{red}
\item Perhaps as a backup slide-> put a slide with the estimated coefficients, NOT exponents
\item depending if time>I can copy it as image from the draft paper or copy the tables, separately each subsample
\end{itemize}
\color{black}
\end{frame}

\begin{frame}\label{MarginalEffects}

\frametitle{Marginal Effects}
\begin{figure}
    \includegraphics[width = 0.6\textwidth]{Figure1a_1f.pdf}
\end{figure}
